### 2017-04-08 src/stats5.tex
Added "Estimation" to SS5.

    \newpage
    \subsection{Confindence interval for varience}

>>>>

    \newpage
    \subsection{Confindence interval for varience}
        For a random sample of $N(\mu, \sigma^2)$ it can be shown that $\displaystyle\frac{(n-1)s^2}{\sigma^2} \sim \chi^2_{n-1}$ where $n$ is the sample size. Using this we can rearrange the result to find the confidence interval for varience.

        \begin{example}
        {
            Calculate a 95\% confidence interval for the mean and variance of the set: 266, 254, 215, 220, 253, 230, 216, 248, 234, 244.
        }

        \begin{step}{Find the mean and variance}
        \begin{align*}
        \bar{x} &= 238 \\
        s^2 &= 313.111
        \end{align*}
        \end{step}

        \begin{step}{Rearrange to find the confidence interval}
        $$\chi^2_9(0.975) < \frac{(n-1)s^2}{\sigma^2} < \chi^2_9(0.075)$$
        $$\chi^2_9(0.975) < \frac{9 \times 313.111}{\sigma^2} < \chi^2_9(0.075)$$
        $$\frac{9 \times 313.111}{\chi^2_9(0.975)} < \sigma^2 < \frac{9 \times 313.111}{\chi^2_9(0.075)}$$
        $$148.128 < \sigma^2 < 1043.553$$
        $$(148.128, 1043.553)$$
        \end{step}
